Forecasting the 2024 U.S. Presidential Election

### 2024-10-24 paper/paper.qmd
Abstract edit

---
title: "Forecasting the 2024 U.S. Presidential Election"
subtitle: "My subtitle if needed"
author: 
  - Tim Chen
  - Steven Li
  - Tommy Fu
thanks: "Code and data are available at: https://github.com/timchen0326/US_presidential_election_forecast_2024.git"
date: today
date-format: long
abstract: "This paper presents a statistical model for forecasting the outcome of the 2024 U.S. Presidential Election. Using polling data from FiveThirtyEight, we develop multiple linear regression models to predict the percentage of support for the main candidates, Kamala Harris and Donald Trump, in different states. We aggregate these predictions to simulate the Electoral College vote and estimate the likelihood of either candidate winning. Our results suggest that neither candidate currently secures the required 270 electoral votes to win the presidency."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
editor: 
  markdown: 
    wrap: sentence
---

@@

- **Pollster rating (Pollscore):** A numerical score reflecting the reliability and historical accuracy of each polling organization.
- **Sample size:** The number of respondents included in each poll, which influences the poll's margin of error.
- **Support percentage (pct):** The percentage of respondents expressing support for each candidate.
- **State:** The U.S. state where the poll was conducted, or in some cases, national-level polling data.

@@

set.seed(123)
# Select key variables and sample for the table
data_overview <- data %>%
  select(poll_id, pollster, pollscore, sample_size, pct, state, 
         candidate_name, end_date) %>% sample_n(5)

colnames(data_overview) <- c("Poll ID", "Pollster", "Pollscore", "Sample Size",
                             "pct", "State", "Candidate", "End Date")

@@

According to our models, neither candidate secures the 270 Electoral College votes needed to win.
Kamala Harris is projected to receive 216 electoral votes, while Donald Trump is predicted to win 147 electoral votes.
However, due to the lack of 270 electoral votes for either candidate, the election remains highly competitive, and further developments may shift the balance.

@@

Electoral College Forecast Aggregating state-level predictions into Electoral College votes demonstrates the potential competitiveness of the 2024 U.S.
Presidential Election.
According to the predictions, neither Kamala Harris nor Donald Trump currently secures the necessary 270 electoral votes to win.
Harris is projected to receive 216 electoral votes, while Trump is predicted to receive 147 electoral votes.
This forecast suggests that the election remains highly uncertain, with several key battleground states likely determining the final outcome.

>>>>

---
title: "Forecasting the 2024 U.S. Presidential Election"
subtitle: "My subtitle if needed"
author: 
  - Tim Chen
  - Steven Li
  - Tommy Fu
thanks: "Code and data are available at: https://github.com/timchen0326/US_presidential_election_forecast_2024.git"
date: today
date-format: long
abstract: "Analysis of polling data from July to October 2024 reveals significant challenges in forecasting the U.S. presidential election between Kamala Harris and Donald Trump, with state-level variations and pollster methodology playing crucial roles in prediction accuracy. Using multi-linear regression models incorporating pollster ratings, sample sizes, and state-level data, we find that Harris is projected to receive 216 electoral votes while Trump is predicted to secure 147 electoral votes. State-level polling variations and methodological differences among pollsters significantly impact predicted outcomes, with pollster reliability metrics explaining substantial variance in candidate support levels. These findings highlight the continued importance of refining polling methodologies and expanding state-level coverage to improve electoral forecasting accuracy, particularly in an era of increasing political polarization."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
editor: 
  markdown: 
    wrap: sentence
---

@@

- **Pollster rating (Pollscore):** A numerical score reflecting the reliability and historical accuracy of each polling organization.
- **Sample size:** The number of respondents included in each poll, which influences the poll's margin of error.
- **Support percentage (pct):** The percentage of respondents expressing support for each candidate.
- **State:** The U.S. state where the poll was conducted, or in some cases, national-level polling data.
- ...

@@

set.seed(123)
# Select key variables and sample for the table
data_overview <- data %>%
  select(poll_id, pollster, pollscore, numeric_grade, transparency_score,
         sample_size, pct, state, methodology, candidate_name, end_date
         ) %>% sample_n(5)

colnames(data_overview) <- 
  c("Poll ID", "Pollster", "Pollscore", "Numeric Grade", "Transparency Score", 
    "Sample Size", "pct", "State", "Methodology", "Candidate", "End Date")

@@

According to our models, Kamala Harris is projected to receive 216 electoral votes, while Donald Trump is predicted to win 147 electoral votes.

@@

Electoral College Forecast Aggregating state-level predictions into Electoral College votes demonstrates the potential competitiveness of the 2024 U.S.
Presidential Election.
Harris is projected to receive 216 electoral votes, while Trump is predicted to receive 147 electoral votes.
This forecast suggests that the election remains highly uncertain, with several key battleground states likely determining the final outcome.
